\newglossaryentry{Naturla Language Processing}
{
    name=Natural Language Processing,
    description={Domain that aims to make machines understand our language and thus making it possible to communicate with them in our own language.}
}
 
\newglossaryentry{Word Sense Induction and Disambiguation}
{
    name=Word Sense Induction and Disambiguation,
    description={Natural Language Processing tasks dealing with finding and assigning correct senses to words}
}

\newglossaryentry{Distributional Hypothesis}
{
    name=Distributional Hypothesis,
    description={Hypothesis stating that words that occur in the same contexts tend to have similar meanings.}
}

\newglossaryentry{Lexical Context}
{
    name=Lexical Context,
    description={Neighborhood of a word as determined by its surrounding words.}
}
\newglossaryentry{Syntactic Context}
{
    name=Syntactic Context,
    description={Neighborhood of a word as determined by the dependency or constituency relations it participates in.}
}
%\newglossaryentry{Vector Space Model}
%{
%    name=,
%    description={}
%}
\newglossaryentry{Network}
{
    name=Network,
    description={Also referred as a graph, structure that links (via edges) entities together (represented by nodes).}
}
\newglossaryentry{Network Model}
{
    name=Network Model,
    description={In this thesis, a graph-based framework that relates words, or other text units, according to different linguistic features.}
}
\newglossaryentry{Data Sparsity}
{
    name=Data Sparsity,
    description={Common in textual data, the phenomenon of having large quantities of zero-valued features representing textual units.}
}

\newglossaryentry{Lexical Co-occurrence Networks}
{
    name=Lexical Co-occurrence Networks,
    description={A network of words linked by the co-occurrent neighboring words.}
}

\newglossaryentry{Semantic Networks}
{
    name=Semantic Networks,
    description={A network of words linked by means of their semantic relations.}
}
\newglossaryentry{Syntactic Co-occurrence Networks}
{
    name=Syntactic Co-occurrence Networks,
    description={A network of words linked according to the role they play in constituency and dependency relations.}
}
\newglossaryentry{Heterogeneous Networks}
{
    name=Heterogeneous Networks,
    description={A network of words linked by different types of linguistic relations (e. g., syntactic, lexical, or semantic). }
}

\newglossaryentry{Spectral Clustering}
{
    name=Spectral Clustering,
    description={Clustering method that makes use of the eigenvalues of a similarity matrix of the data to perform dimensionality reduction before clustering in fewer dimensions.}
}

\newglossaryentry{Structured Perceptron}
{
    name=Structured Perceptron,
    description={A supervised sequence classifier, it consists on coupling a perceptron with the Viterbi decoder algorithm to determine the most appropriate sequence of tags.}
}

\newglossaryentry{Hypergraph}
{
    name=Hypergraph,
    description={A graph generalization that allows more than two vertices to be linked by a single edge.}
}

\newglossaryentry{Dependency Tree}
{
    name=Dependency Tree,
    description={A dependency parse links words together according to their syntactic relations. Each node in the tree represents a word, child nodes are words that are dependent on the parent, and edges are labeled by the relationship.}
}

\newglossaryentry{Constituency Tree}
{
    name=Constituency Tree,
    description={This analysis breaks a text into sub-phrases. Non-terminals in the tree are types of phrases, the terminals are the words in the sentence, and the edges are unlabeled.}
}

\newglossaryentry{Fusion Techniques}
{
    name=Fusion Techniques,
    description={Set of operators conceived to combine different representation spaces into a single, more dense, one.}
}

\newglossaryentry{Named Entity Recognition}
{
    name=Named Entity Recognition,
    description={A task of Natural Language Processing, its goal is to detect mentions of named entities within a written text. The classic types of entities are: organization, person, and location.}
}